Random Forests", OAs

### 2024-01-27 src/oa_RF.Rmd
for bham presentation

varimp_mars <- varImp(model.all) 
varimp_mars$importance <- varimp_mars$importance %>% 
  rownames_to_column() %>% 
  mutate(rowname = ifelse(rowname == "dist", "distance to the nearest city",
                          ifelse(rowname == "dist.retail", "distance to the nearest retail centre", 
                                 ifelse(rowname == "London", "distance to London",
                                        ifelse(rowname == "n.nearest.retail.lag", "Nearest retail centre's web density, t-1",
                                               ifelse(rowname == "n.London.lag", "London's web density, t-1",
                                                      ifelse(rowname == "n.l.slag", "spatial and temporal lag of web density",
                                                             ifelse(rowname == "n.nearest.city", "Nearest city's web density, t-1", rowname)))))))) %>% 
  column_to_rownames()

>>>>

varimp_mars <- varImp(model.all) 
varimp_mars$importance <- varimp_mars$importance %>% 
  rownames_to_column() %>% 
  mutate(rowname = ifelse(rowname == "dist", "distance to the nearest city",
                          ifelse(rowname == "dist.retail", "distance to the nearest retail centre", 
                                 ifelse(rowname == "London", "distance to London",
                                        ifelse(rowname == "n.nearest.retail.lag", "Nearest retail centre's wensite density, t-1",
                                               ifelse(rowname == "n.London.lag", "London's wensite density, t-1",
                                                      ifelse(rowname == "n.l.slag", "spatial and temporal lag of wensite density",
                                                             ifelse(rowname == "n.nearest.city", "Nearest city's wensite density, t-1", rowname)))))))) %>% 
  column_to_rownames()
